\documentclass[12pt]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{graphics}
\usepackage{qtree}
\usepackage{tikz}
\usepackage[utf8]{inputenc} % æøå
\usepackage[T1]{fontenc} % mere æøå
\usepackage[danish]{babel} % orddeling
\usepackage{verbatim} % så man kan skrive ren tekst
\usepackage[all]{xy} % den sidste (avancerede) formel i dokumentet
\usepackage{fullpage} % mindre margin

\title{ProjDat 2014\\Props 2.0}
\author{Louise Knudsen (140791 - zsh845)\\
Helena Bach (180492 - wzg314)\\
David Pedersen (060890 - tlb209)\\\\
Instructor: Simon Shine }
\date{\today}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}

\newcommand{\og}{\wedge}

\begin{document}
\maketitle
\newpage
\section{Program- and systemtest}
The amount of testing we have done at this moment is very limited because we don't have any code yet to test. We have however discussed how we will structure the testing when we start coding.
\newline
\newline
We intend to use Test Driven Development when developing the system. This means that tests will be written before the implementation code is written. This weaves the test plan and implementation plan together. There will not be a dedicated time period in which we do the testing and there will not be a defined set of resources (developers) in charge of doing the testing. People will test their code as they write it and modify the tests accordingly when changing the code.
\newline
\newline
We don't have any test case specifications, a test incident report, or a test report summary, since we don't yet have any tests.
\end{document}
